Palomar 5 Gaps

### 2024-09-20 paper/main.tex
starting the results

  \subsection{Gap detection}

@@

@@

    To understand how the impacted particle is perturbed, one needs to compute its change in momentum, which is determined by integrating the force acting on the particle over the duration of the interaction. A useful approximation for this change in momentum is the force at the closest approach multiplied by an estimate of the interaction time:
    \begin{equation} 
      \Delta p \approx \text{Force} \times \text{interaction time} = \frac{GMm}{b^2} \times \frac{b}{v} = \frac{GM}{bv}, 
      \end{equation}
    where $M$ is the mass of the perturber, $m$ is the mass of the particle, $b$ is the impact parameter, $v$ is the relative velocity of the perturber with respect to the particle, and $G$ is the gravitational constant.

@@

@@

  \begin{figure*}
    \centering
    \includegraphics[width=\linewidth, trim=20 0 15 0]{monte-carlo-009-pouliasis2017pii-GCNBody-2000-milisigma-5-noisefactor-20-boxcarindexlength-shifted-0.png}
    \caption[]{A comparison between the vanilla and full simulations. This showcases our gap detection method, in which the 2D maps in \textit{tail coordinates} are inspected, and their 1D marginalized density distributions are compared quantitatively. The $x'$ coordinate indicates distance from the center of mass of Pal5 along it's orbit. The two profiles are subtraced in locations where the signal is above the noise threshold, and locations that are more that are underdense by 2-$\sigma$ are highlighted with vertical blue lines, and labeled \textit{gap candidate}. This also showcases the limitation in this 1D profile method since a very skinny and oblique gap is present, whose signal is washed out from marginalizing.}
    \label{fig:profiles}
    \end{figure*}

@@

  \section{Gallery of Gaps}

>>>>

  \subsection{Gap detection} \label{sec:gap_detection}

@@

      \begin{figure*}
        \centering
        \includegraphics[width=\linewidth, trim=20 0 15 0]{monte-carlo-009-pouliasis2017pii-GCNBody-2000-milisigma-5-noisefactor-20-boxcarindexlength-shifted-0.png}
        \caption{A comparison between the density maps and profiles of the \textit{full} and \textit{vanilla} simulations is presented. The locations where the full simulation is less dense than the vanilla simulation by 2-$\sigma$ is highlighted by blue vertical bars. Bins below the noise threshold are not considered when measuring the differences between the two 1D profiles. The 1D profiles have been smoothed with a median box-car filter.}
        \label{fig:profiles}
        \end{figure*}

@@

    To understand how the impacted particle is perturbed, one needs to compute its change in momentum, which is determined by integrating the force acting on the particle over the duration of the interaction. A useful approximation for this change in momentum is the force at the closest approach multiplied by an estimate of the interaction time:
    \begin{equation} 
      \Delta p \approx \text{Force} \times \text{interaction time} = \frac{GMm}{b^2} \times \frac{b}{v} = \frac{GM}{bv}, 
      \end{equation} \label{eq:change_in_momentum}
    where $M$ is the mass of the perturber, $m$ is the mass of the particle, $b$ is the impact parameter, $v$ is the relative velocity of the perturber with respect to the particle, and $G$ is the gravitational constant.

@@

  One of the 50 simulations is shown in Fig.~\ref{fig:stream_on_sky}--which we selected for its clear and prominent gaps which is visibile when considering the scatter plot of the stars on the sky and becomes even more apparent when marginalizing over latitutde to see it's 1D density over longitude.

  We then transformed the stream to tail coordinates for the both the \textit{vanilla} and \textit{full} simulations in Fig.~\ref{fig:profiles}. As described in section~\ref{sec:gap_detection}, we locate regions on the stream where the full simulations are significantly less dense than the vanilla simulations. Notice the \textit{Tiny Gap} labeled in the middle plot. This signal is not present in the 1D profile since it is too small in size and at an oblique angle, thus is lost when marginalizing. This process was followed for all 50 simulations to identify possible gaps. We find that small gaps are identifiable by eye rather well, where the 1D profiles aid in finding subtle yet extended underdensities. All simulations and labeled gaps are presented in the Appendix~\ref{appendix:gallery_of_gaps}. The profile method was useful in identifying the gaps in sampling 002, 006, 008, 029, 030.

@@

@@

  \section{Gallery of Gaps} \label{appendix:gallery_of_gaps}
